---
title: "sanson-v-hwk2-1"
output: pdf_document
date: "2023-02-06"
---
---
title: "ECON 470 Homework 2"
author: "Virginia Sanson"
output: pdf_document
date: "2023-02-11"
---

```{r setup, include=FALSE}
load("Hwk2_workspace.Rdata")
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, ggplot2, dplyr, lubridate, stringr, readxl, data.table, gdata, scales,
               kableExtra)
```

\vspace{.2in}
\noindent Question 1

2,114 hospitals filed more than one report in the same year, from 1997 to 2018. 

```{r graph1, echo=F}

print(graph1)

```
\vspace{.2in}
\noindent Question 2

The total number of unique hospital IDs in the dataset is `r unique_provider_numbers`. 


\vspace{1.5in}
\noindent Question 3

```{r graph2, echo=F}

print(graph2)

```

\noindent Question 4
```{r graph3, echo=F}

print(graph3)

```

\vspace{.2in}
\noindent Question 5
```{r table5, echo=F}

print(table5)

```

\vspace{.2in}
\noindent Question 6

```{r table6, echo=F}

print(table6)

```

\vspace{.2in}
\noindent Question 7



